%!TEX root = /Users/jakubkonka/Thesis/Thesis.tex
\chapter{Intelligent Network Selection} % (fold)
\label{cha:intelligent}

\minitoc
\vspace{10mm}

\section{The Problem of Intelligent Network Seletion} % (fold)
\label{sec:the_problem_of_intelligent_network_seletion_intelligent}

% section the_problem_of_intelligent_network_seletion_intelligent (end)

\section{Intelligent Network Selection in the Literature} % (fold)
\label{sec:intelligent_network_selection_in_the_literature_intelligent}
Over the last decade, several papers have explored the problem of intelligent network selection in heterogeneous wireless access networks. Wang and Kuo provide an up-to-date survey of the mainstream approaches to the network selection problem covering: utility and game theory, fuzzy logic, multiple attribute decision making, combinatorial optimization, and Markov chains \cite{LushengKuo2013}. Liu \emph{et al.}, propose an algorithm for optimal network selection which mainly aims at optimizing energy consumption of the user equipment \cite{Liu2009}. Espi~\emph{et al.} present a machine learning approach to network selection; in particular, the authors utilize a Hopfield neural network to solve the underlying optimization problem \cite{Espi10}. Antoniou \emph{et al.}, and Charilas \emph{et al.}~model the problem as a noncooperative game between wireless access networks with the aim of obtaining the best possible trade-off between the efficiency and the available capacity of networks, while, at the same time, satisfying the requested quality by the subscribers \cite{Antoniou07, Charilas08}. Ormond \emph{et al.}~propose an algorithm for cost-oriented and performance-aware network selection that maximizes consumer surplus \cite{OrmondCS106, OrmondCS206}. Niyato \emph{et al.}~propose two algorithms based on evolutionary game theory for a network selection mechanism which performs intelligent load balancing so that network congestion and performance degradation can be avoided \cite{Niyato09}. Addtionally, the same authors model the user churning behavior in heterogeneous wireless access networks using evolutionary game theory \cite{NiyatoHossainConf2008}. Khan \emph{et al.}~model the problem as a procurement second-price sealed-bid auction where network operators bid for the right to service the subscriber's request \cite{Khan110, Khan210}. Zhu \emph{et al.}~build upon the work reported in~\cite{Niyato09}, and explore the dynamics of network selection, using Bayesian evolutionary game theory, in an environment where subscribers have only limited (incomplete) information about each others preferences \cite{ZhuNiyato2010}. Finally, Irvine \emph{et al.}~propose a market-based framework called the Digital Marketplace where network operators compete in a variant of a procurement first-price sealed-bid auction for the right to transport the subscriber's requested service over their infrastructure \cite{DMLeBodic00, DMIrvine01, DMIrvine02}.
% section intelligent_network_selection_in_the_literature_intelligent (end)

\section{Approaches Considering Economic Aspects} % (fold)
\label{sec:approaches_considering_economic_aspects_intelligent}

% section approaches_considering_economic_aspects_intelligent (end)

\section{Summary} % (fold)
\label{sec:summary_intelligent}

% section summary_intelligent (end)
% chapter intelligent (end)
