%!TEX root = /Users/jakubkonka/Thesis/Thesis.tex
\chapter{Conclusions and Further Work}
\label{cha:conclusions}

\section{Conclusions} % (fold)
\label{sec:conclusions_conclusions}
The world of mobile communications is becoming increasingly diverse in terms of different wireless access technologies available: WiFi, 3G, and the cutting-edge 4G are gradually being rolled out in many countries across the world. In an environment of such diversity and heterogeneity, where each wireless access technology has its own distinct characteristics, intelligent network selection provides a resource efficient way of handling communications services by matching the services' required quality with the characteristics of a particular access technology.

To make full use of this increasingly diverse environment and increase the competition between network operators even further, the one-to-one mapping between network operators and subscribers need no longer hold. This allows the subscribers to seamlessly switch not only between different wireless access technologies belonging to one particular network operator, but also between network operators themselves. In this way, the subscriber, when requesting a service, is given the option to select a network operator and a wireless access technology that best matches the required quality requirements of the service. It is not only to the benefit of the subscribers, however, since the integration of wireless access technologies will allow network operators for improved revenue generation, and more efficient usage of network resources.

This thesis explored the economic aspects of intelligent network selection. The problem was studied within the context of Digital Marketplace---a \annotate{C3.5}{theoretical} market-based framework \annotate{C1.5}{for trading wireless communications services. It was first proposed by Irvine~\emph{et al.}~in 2000~\cite{DMLeBodic00,DMIrvine00}, and it was developed with the heterogeneous wireless communications environment in mind, where the subscribers have the ability to select a network operator that reflects their preferences on a per service basis.} Since the Digital Marketplace was created with free market (or ``perfect'' competition) in mind, it is particularly well-suited towards the management of future wireless environment where wireless access is traded on a per service basis. It is for this reason that this research explored the problem of network selection within the context of Digital Marketplace.

The network selection mechanism advocated by the Digital Marketplace lacked extensive and rigorous economic analysis. With the game theoretic analysis presented in this thesis, this deficiency has been addressed. More specifically, in Chapter~\ref{cha:direct}, \annotate{C7.3}{a game-theoretic model of the network selection mechanism was formally defined. Several simplifying assumptions were made in order to keep the analysis mathematically tractable. For example, the network operators and the subscriber are risk neutral, and the subscriber does not have any budget constraints. Despite the fact that those assumptions are not entirely representative of the reality, following in the footsteps of von Neumann and Morgenstern, the mathematical theory of an economic phenomenon should be rigorous and developed gradually~\cite{VonNeumann2004}. Therefore, the simplifying assumptions made in this chapter and thesis serve as a starting point for the rigorous, gradual development of the economic theory of operation of the network selection mechanism in the Digital Marketplace, before it can embark on capturing the reality to a high degree.}

Furthermore, in the chapter, the equilibrium bidding strategies were derived for three special/extreme cases. In the first case, when only reputation ratings of the network operators decide on the winning network operator, it was shown that network operators will find it beneficial to submit abnormally high bids, since their bid is independent of the probability of winning the auction. \annotate{C7.3}{While this result sounds like a potential design flaw, in reality, the subscribers will necessarily be budget constrained, and therefore, abnormally high bidding of the network operators will translate into charging the subscribers a premium price for the service that is within the limits of their respective budgets.} In the second case, when only the monetary bids of the network operators matter in the selection of the winner, it was shown that the problem reduces to a standard first-price sealed-bid auction with symmetric bidders, and therefore, the symmetric equilibrium bidding strategies of the standard first-price sealed-bid auction applies. Similarly, the third case, when all network operators are characterised by the same reputation rating, was shown to be a special case of the second case. \annotate{C7.3}{In both cases, the abundance of theoretical results and economic insight from the auction literature applies, found, for example, in Krishna~\cite{Krishna10}.}

Finally, the equilibrium bidding strategies for only two network operators were analytically derived. It was shown that although the derived equilibium bidding strategies allows for negative bids, it does not lead to negative profit in case of winning (or a tie) of either network operator. In fact, it was established that the direct mechanism representation of the Digital Marketplace auction satisfies both individual rationality and incentive compatibility constraints. As a result, this proved that the network operators would find it in their best interest to participate in the auction, and they would reveal their costs truthfully. \annotate{C7.3}{It was further noted that the real behaviour of the network operators might be dictated by the need to secure the contract with the subscriber first and foremost, and hence, lead to negative bidding; a strategy akin to the ``loss leader'' pricing strategy. However, since the ultimate aim of this thesis was gradual development of rigorous economic theory of the operation of the network selection mechanism within the Digital Marketplace, network operators were always assumed to behave rationally from the perspective of game theory, and bid at least their cost.}

In Chapter~\ref{cha:indirect}, by mathematically transforming the problem into an alternate form, it was shown that the equilibrium bidding strategies exist and are unique. \annotate{C7.3}{This was an important result from the perspective of the development of rigorous theory of the operation of the network selection mechanism as it proved that the mechanism is economically well-behaved since the equilibrium exists.} Furthermore, the equilibrium bidding strategies were explicitly derived in the case of two network operators and their costs assumed to be uniformly distributed. \annotate{C7.3}{The assumption of uniform distribution of costs for the network operators was argumented by the fact that it is a standard practice when there is a lack of knowledge of the actual type of the distributions~\cite{Chung2004}. Nevertheless, it was noted that such an assumption is limiting, and it is highly likely it will not be fully representative of the reality.} Furthermore, in the case of two network operators, the expected prices the subscribers will have to pay for different values of the price weight were examined. \annotate{C7.3}{It was shown that, for any expected price, as the difference between the reputation ratings of the network operators increases, the price weight has to increase (or remain constant) in order to keep the expected price fixed. It was noted that this observation carries very serious implications on the operation of the Digital Marketplace, as the subscriber is effectively given the ability to influence the expected prices by an appropriate choice of the price weight.}

Finally, three numerical methods for numerically approximating the equilibrium bidding strategies in the case of more than two network operators were proposed: forward shooting method (FSM), polynomial projection method (PPM), and extended FSM (EFSM). \annotate{C7.3}{When developing the algorithms, similarly to the restricted case with two network operators, it was assumed that costs for the network operators were uniformly distributed; therefore, the same limitations applied. However, generalising the algorithms to nonuniform distributions should not prove difficult since other researchers have successfully employed similar numerical methods for studying problems where distributions were nonuniform~\cite{HubbardPaarsch2011}.} The FSM and PPM methods allow for numerically approximating equilibrium bidding strategies for a subset of all possible bidding scenarios resulting in nontrivial equilibria, while the EFSM method enables computation of the numerical solution to all bidding scenarios. It should be noted at this point that the development of the EFSM method constitutes an indirect contribution of this thesis. The method allows for approximating solution to first-price sealed-bid auction with asymmetric bidders posed by the Digital Marketplace bidding problem, and to the best of the author's knowledge, this type of auctions has not yet been solved numerically by the economic community. \annotate{C7.3}{Since the analytical derivation of the equilibrium bidding strategies in the case of more than two network operators is not possible, the existence of algorithms capable of numerically approximating the solutions is a major step forward in the development of the economic theory of operation of the network selection mechanism in the Digital Marketplace. Furthermore, the algorithms constitute a tool that the network operators participating in the Digital Marketplace can use to formulate their own bidding strategies, and understand the bidding behaviours of other network operators.}

\annotate{C7.3}{It is a well-known fact that the FSM method and its derivatives, such as the EFSM method, become numerically unstable for large number of bidders~\cite{FibichGavish2011}. While this issue did not impact the results presented in the thesis (due to the fact that only as many as five network operators were considered), it is important to acknowledge the fact that the issue exists. Therefore, in order to address the problem of numerical instability, Chapter~\ref{cha:approximation} explored whether an auction format represented by the network selection mechanism employed in the Digital Marketplace can be modelled as an auction with common prior.} In an auction with common prior, the range the costs can vary is the same for each bidder. To this end, the methodology for casting the bidding problem posed by the Digital Marketplace into the auction with common prior was presented, and the methodology for quantifying the accuracy of the approximation was outlined. Finally, the chapter concluded with the presentation of approximation results for four bidding scenarios with two, three, four and five bidders respectively. It was shown that approximating the network selection mechanism employed by the Digital Marketplace with an auction with common prior consitutes a valid alternative, and as such, even though not perfectly accurate (mean relative errors as large as almost 16\% for all bidders), it might be a more desirable option for the network operators due to the wealth of numerical methods available that have been extensively studied by the researchers.

\annotate{C7.1}{To conclude, the work reported in this thesis constitutes the first step towards the development of rigorous economic theory of the operation of the network selection mechanism in the Digital Marketplace. As such, the participating network operators can use the results derived in this thesis to formulate their pricing strategies and understand the bidding behaviour of their opponents. The subscribers, on the other hand, are in the position to understand the prices they will be required to pay depending on their preferences for the requested service (in terms of the price weight) and the reputation ratings of the participating network operators. However, due to the fact that many simplifying assumptions had to be made in order to develop the theory, it will not be fully representative of the reality, and therefore, the results presented herein should be taken ``with a grain of salt''.}
% section conclusions (end)

\section{Further Work} % (fold)
\label{sec:further_work_conclusions}
There are many aspects of the research presented in this thesis that can further be elaborated upon. The most important future directions are as follows.

\subsection{Dynamic Aspect of the Network Selection Mechanism}
\label{sub:dynamic_aspect_of_the_network_selection_mechanism}
This thesis did not consider the temporal aspect of the network selection mechanism. In game-theoretic terms, the game was assumed to be static as opposed to dynamic. In other words, it was assumed that if the network operators were to interact in an auction more than once, they would discount any previous, historic interactions. This limits the applicability of the results presented in this thesis to real-life scenarios for two main reasons.

\annotate{C7.2}{Firstly, treating the game as static ignores the forces of supply and demand that necessarily exist in the market, and ignores the possibility of existence of market equilibrium (regardless of whether it is actually achievable)~\cite{MicroTheory}.} Indeed, the physical medium (i.e., the radio frequency spectrum) which facilitates distribution of wireless communications services has finite capacity, and therefore, on many occassions, supply may outweigh demand, or in less populated areas, demand may outweigh supply~\cite{LeCadre2009}. While the problem of matching supply and demand in wireless communications markets is not as critical as in electricity markets where imbalance may damage the entire electricity network, it is important to consider as it will affect the subscribers' experience with the services received~\cite{Lincoln2011}.

Secondly, as discussed by Figliozzi~\emph{et al.}, repeated interaction of bidders in an auction will inevitably lead to information revelation and learning by the bidders~\cite{FigliozziJaillet2008}. For example, if it was assumed that the bids are disclosed to all network operators after the auction concludes, this would inevitably lead to network operators inferring the cost structure of other network operators, and hence, induce bidding strategies that diverge from the equilibrium bidding strategies derived in this thesis.

\subsection{Relaxing Fundamental Assumptions}
\label{sub:relaxing_fundamental_assumptions_conclusions}
The results presented in this thesis are based on the following fundamental assumptions: 1) subscriber does not have any budget constraints; 2) subscriber and network operators are risk neutral; and 3) network operators are characterised by symmetric cost distributions (see Section~\ref{sec:problem_definition_and_assumptions_direct}, Chapter~\ref{cha:direct}). It is generally agreed that these assumptions do not reflect the real world to a high degree~\cite{Krishna10}.

To elaborate further, by enforcing budget constraints on the subscriber, the theory developed in this thesis would be in a better position to rigorously put a limit on abnormally high bidding of network operators stated in Proposition~\ref{prop:special_case_w_0_direct}, which otherwise had to be speculated. Secondly, the assumption of risk neutrality is theoretically desirable as it implies that the expected payoff of a bidder is additively separable, and hence, easier to handle mathematically~\cite{Krishna10}. However, risk aversion, which assumes that bidders are more likely to accept a certain outcome rather than embrace the uncertainty and gamble, may be a more credible assumption~\cite{Liu2003}. Finally, the last assumption supposes that the network operators are \emph{ex ante} identical, and, as argued by Guth~\emph{et al.}~for example, it is violated in many real-life auction environments. Thus, it should be dropped in favour of more credible assumption that the network operators are characterised by asymmetric cost distributions. 

It is important to notice, however, that the reason those assumptions were incorporated in this research in the first place was to retain the mathematical tractability. With those assumptions relaxed, this is no longer guaranteed, and hence, it gives rise to a tradeoff between mathematical tractability and applicability to real-world scenarios.

\subsection{Subscriber's Perspective: Expected Prices}
\label{sub:subscribers_perspective_expected_prices_conclusions}
This thesis examined the expected prices only in the case of two network operators (see Section~\ref{sub:subscriber_s_perspective_expected_prices_indirect}, Chapter~\ref{cha:indirect}). Since the UK market is currently dominated by an oligopoly of four incumbent network operators who own their infrastructure (EE, Vodafone, O2, and Three), examining the expected prices for more than two network operators is directly relevant.

It should be noted that deriving the expected prices should be fairly straightforward to execute. All that is required is to treat the numerically approximated equilibrium bidding strategies (generated using EFSM method, or otherwise) as the input to Algorithm~\ref{alg:inverse_of_equilibrium_inverse_bidding_strategy_functions_indirect}, and proceed according to the methodology presented in Section~\ref{sub:subscriber_s_perspective_expected_prices_indirect}, Chapter~\ref{cha:indirect}.

An analysis of expected prices in scenarios with more than two network operators would be of benefit not only to the subscribers involved in the Digital Marketplace, but also to the system designer/market provider. With the characterisation in place, it would then be possible to verify whether the subscribers are still able to influence the expected prices by an appropriate choice of the price weight like in the case of only two network operators (see Section~\ref{sub:subscriber_s_perspective_expected_prices_indirect}, Chapter~\ref{cha:indirect}).

\subsection{Generalising Extended Forward Shooting Method}
\label{sub:generalising_extended_forward_shooting_method_conclusions}
The implementation of the EFSM method assumes the bidders to be characterised by uniform distributions of costs (see Section~\ref{sub:extended_forward_shooting_method_indirect}, Chapter~\ref{cha:indirect}). As discussed in the thesis, uniform distributions are an appropriate assumption given the lack of knowledge of the way the costs are distributed. However, should the Digital Marketplace and the network selection mechanism presented in this thesis be used in practice, the market participants may acquire knowledge that will conflict with the assumption of uniformly distributed costs~\cite{Chung2004}. Therefore, it will strengthen the generality of the results presented in this thesis if the EFSM method is implemented for bidders characterised by nonuniform distributions as well.

Furthermore, generalising the EFSM method to nonuniform distributions would make it applicable to problems beyond the Digital Marketplace. To the best of the author's knowledge, the EFSM method is the only numerical algorithm in existence that numerically solves the unusual first-price sealed-bid auction with asymmetric bidders posed by the Digital Marketplace bidding problem. As such, it would constitute a major contribution to the field of computational auction theory.

\subsection{Different Distributions in Common Prior Auction}
\label{sub:different_distributions_in_common_prior_auction_conclusions}
It is a well-known fact that the FSM method and its derivatives, such as the EFSM method, become numerically unstable for large number of bidders~\cite{FibichGavish2011}. In order to address the problem of numerical instability, this thesis explored whether an auction format represented by the network selection mechanism employed in the Digital Marketplace can be modelled as an auction with common prior.

Casting the auction format represented by the network selection mechanism employed in the Digital Marketplace into an auction with common prior assumes that the latter is based on truncated normal distributions (see Section~\ref{sec:network_selection_mechanism_cast_into_common_priors_setting_approximation}, Chapter~\ref{cha:approximation}). However, this assumption generated an approximation error as large as 16\%. It should be explored whether utilisation of different distributions would decrease the error. A natural starting point would be to test truncated normal distributions with different mean and standard deviation parameters. But the investigation is not limited to this particular family of distributions since there exist many distributions that could be used in their place; for example, truncated log-normal distributions.
% section further_work (end)
